A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-07-23 07_Manuscript.Rmd
Insert Lambrides2007 mungbean ref
This is a better reference to use than Pulse AU

Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown in south-east Asia for human consumption as an affordable source of protein [@PulseAustralia].
The bean pod or grain can be consumed raw or added to meals after sprouting.
The dried grain can also be ground into a protein enriched flour for uses such as noodles, biscuits and cakes [@Chankaew2013].

>>>>

Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown in south-east Asia for human consumption as an affordable source of protein [@Lambrides2007].
The bean pod or grain can be consumed raw or added to meals after sprouting.
The dried grain can also be ground into a protein enriched flour for uses such as noodles, biscuits and cakes [@Chankaew2013].
